MSPMS Report

### 2024-06-07 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
Changed github actions to work in develop branch and polished some of the plotting functions.

**Figure 4.** Here the cleavage motifs enriched in each condition are shown.

>>>>

**Figure 4.** Here the cleavage motifs enriched in each condition are shown. 
Enriched cleavage motifs are defined as having a p.adj <= 0.05 and a log2fc >3
relative to time 0.

# Position Specificity

```{r}
sig = t2 %>% 
  filter(p.adj <= 0.05, log2fc >3)

d = count_cleavages_per_pos(sig)

plot_cleavages_per_pos(d)
```

**Figure 5.** Here the count of significant cleavages at each position of the 
peptide library are shown for each condition (facet) per time point (color). 
Significant cleavages are defined as having a p.adj <= 0.05 and a log2fc > 3 
relative to time 0.
